---
title: "00_Analysis_pre"
---

# Set Parameters
```{r}
library(readr)
library(haven)
library(dplyr)
library(ggplot2)
library(DataExplorer)
library(patchwork)

custom_theme <- theme(
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  axis.text = element_text(size = 12),
  axis.title = element_text(size = 12, face = "bold"),
  axis.line = element_line(size = 0.5),
  plot.title = element_text(size = 14, face = "bold", hjust = 0.5)
)

custom_theme2 <- theme(
    panel.grid.major = element_blank(),  # 移除主要网格线
    panel.grid.minor = element_blank(),  # 移除次要网格线
    panel.background = element_blank(),  # 移除面板背景色
    axis.ticks = element_blank(),  # 移除坐标轴刻度
    panel.border = element_rect(colour = "black", fill = NA, size = 1)  # 添加边框
  )
```

# 01-Covariate Clean
## Load V9 Covariates
```{r}
setwd('/Users/gsn/OneDrive - Johns Hopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/')
dat_cov_V9 = read_dta('covariate_V9_derive.dta')

dat_cov_V9_select <- dat_cov_V9 |>
  mutate(Age = v9age91,
         lisr_index = lisr_i92) |>
  select(-bmi91, -racegrp91, -drnkr91, -diabts96,
         -v9age91,-sport_index, -lisr_index,
         -systolic91, -diastolic91, -sppb91,  -sprt_i91,
         -v9date91_followupdays, # no cigt92
         -lisr_i92, -gender)# no cesd91 
# plot_missing(dat_cov_V9_select)
```

### Add Center, Education, Birth
```{r}
## Center
dat_center = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
table(dat_center$center)
colnames(dat_center)[1] = 'subjectid'
dat_center = dat_center |> select(subjectid, center)

dat_cov_V9_select = merge(dat_cov_V9_select, dat_center, 'subjectid', all.x = TRUE)

## Education
dat_edu = read_dta('/Users/gsn/OneDrive - Johns Hopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/education_V1.dta')
table(dat_edu$elevel02)
colnames(dat_edu)[1] = 'subjectid'
dat_edu = dat_edu |> select(subjectid, elevel02)
dat_edu = dat_edu |>
  mutate(Education = factor(
      elevel02,
      levels = c(1, 2, 3),
      labels = c('Less than high school',
                 'High school, GED certification, or vocational schools',
                 'College, graduate, or professional school')))

dat_cov_V9_select = merge(dat_cov_V9_select, dat_edu, 'subjectid', all.x = TRUE)

## Birth
dat_Birth = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
dat_Birth = dat_Birth |> select(id, birthdat, v1date01) |> mutate(subjectid = id) |> select(-id)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_Birth, 'subjectid', all.x = TRUE)

dat_cov_V9_select = dat_cov_V9_select |> mutate(exam_age = (v1date01 - birthdat + exam_dat_V9)/365.25) |>
  select(-v1date01, -birthdat, -elevel02)
```

## Clean Covariates
```{r}
head(dat_cov_V9_select)
plot_missing(dat_cov_V9_select)

dat_cov_V9_select = dat_cov_V9_select |>
  filter(race == 0 | race ==1)
```

## Generate Table 1
```{r}
dat_cov = dat_cov_V9_select
library(dplyr)
head(dat_cov)
colnames(dat_cov)

dat_cov_p1 <- dat_cov %>%
  filter(race %in% c('0','1')) %>%
  mutate(
    Sex = factor(
           sex,
           levels = c("0", "1"),
           labels = c("female", "male")))  %>%
  mutate(
    Race = factor(
      race,
      levels = c("0", "1"),
      labels = c("White", "Black")
    ),
    BMI = factor(
      BMI_cat,
      levels = c("1", "2", "3", "4"),
      labels = c("<=18.5", "18.5~24", "24~28", ">28")
    ),
    Hypertension = factor(
      hypertension,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Diabetes = factor(
      diabetes,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    )
  )  %>%
  mutate(
    SPPB = sppb_score
  )

dat_cov_p1

## Generate Table1 Summary
library(gtsummary)
library(flextable)
colnames(dat_cov_p1)


# t1_v9_SPPB <- dat_cov_p1 %>%
#   select(Age, Sex, Race, BMI, Hypertension,
#          Diabetes, SportIndex, SPPB) %>% 
#   tbl_summary(by = "SPPB",
#               statistic = all_continuous() ~ "{mean}({sd})") %>% 
#   add_overall() %>% 
#   add_p(test = list(all_continuous() ~ "aov", 
#                     all_categorical() ~ "chisq.test")) %>% 
#   as_flex_table() %>%
#   save_as_docx(path = "Results/Table1_v9_SPPB.docx")
```

# 02-PA minute-level data
## Minute-level raw data
```{r}
library(readr)
dat_PA_m.raw = read_csv('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/Actigraph/Wrist Data (V9)/Summary measures/ARIC_V9_ACR_1440_Upto20230316.csv')
colnames(dat_PA_m.raw)[1] = 'subjectid'
head(dat_PA_m.raw, 10)
```

# 03.Generate and combine Step Count
## Missing ID
### Find missing subject ID from Sunan
```{r}
folder_path = 'StepCount/sunan_day_stepcount/'
files = list.files(folder_path)
id_list_analyzed = sub('.csv', '', files)
id_list_sunan = read.csv('file_sunan.csv')

## find missing ID
temp.list = sub('_.*$', '', sub('[F,J,M]', '', id_list_sunan$file_name))
miss.ID = id_list_sunan$file_name[!temp.list %in% id_list_analyzed]

miss_list_sunan = data.frame(miss.ID)
colnames(miss_list_sunan) = 'file_name'
```

### Find missing subject ID from Xinkai
```{r}
folder_path = 'StepCount/xinkai_day_stepcount_raw/'
files = list.files(folder_path)
length(files)
id_list_analyzed = sub('.csv', '', files)
id_list_xinkai = read.csv('file_xinkai.csv')

## find missing ID
temp.list = sub('_.*$', '', sub('[F,J,M]', '', id_list_sunan$file_name))
miss.ID = id_list_xinkai$file_name[!id_list_xinkai$file_name %in% id_list_analyzed]

miss_list_xinkai = data.frame(miss.ID)
colnames(miss_list_xinkai) = 'file_name'
# write.csv(miss_list_xinkai, 'miss_list_xinkai.csv')

## combine Miss_Xinkai and Miss_Sunan
miss_list_all = rbind(miss_list_sunan, miss_list_xinkai)
# write.csv(miss_list_all, 'miss_list_all.csv')
```

## Missing StepCount(Xinkai)
```{r}
folder_path = 'StepCount/Output_Xinkai/'
agge.file = read.csv('StepCount/Output_Xinkai/steps-aggregated.csv')
total.file = read.csv('StepCount/Output_Xinkai/total-steps.csv')
miss.ID = total.file[!rowSums(is.na(total.file)) == 0,]

## Locate Subject ID that miss OAK, SDT and vs
miss.ID.OAK = miss.ID[is.na(miss.ID$oak),] # Need to run OAK, SDT and vs additionally.
write.csv(miss.ID.OAK$id, 'miss_list_OAK.csv')

## Locate Subject ID that miss stepcount
miss.ID.stepcount = miss.ID[is.na(miss.ID$stepcount_rf),]
# write.csv(miss.ID.stepcount$id, 'miss_list_stepcount.csv')
```

## Combine StepCount (Xinkai)
```{r}
folder_path = 'StepCount/xinkai_day_stepcount_raw/'
file.tmp = list.files(folder_path)

## Select ID with -OAK label
ID.tmp.OAK = sub('-OAK.csv', '', file.tmp[grepl('-OAK', file.tmp)])
use.list = c()
for (ID.tmp in ID.tmp.OAK){
  ID = ID.tmp[1]; ID = sub('_.*', '', ID)
  file.name = file.tmp[grepl(ID, file.tmp)]
  dt1 = read.csv(paste0(folder_path, file.name[1]))
  dt2 = read.csv(paste0(folder_path, file.name[2]))
  dt.new = rbind(dt1, dt2)
  dt.new$id = sub('_.*', '', dt.new$id)
  use.list = c(use.list, file.name)
  write.csv(dt.new, paste0('StepCount/xinkai_day_stepcount/', ID, '.csv'))
}

## Select ID with full records
ID.left.1 = setdiff(file.tmp,use.list)
for (ID.tmp in ID.left.1){
  dt1 = read.csv(paste0(folder_path, ID.tmp)); ID = sub('_.*', '', ID.tmp)
  dt1$id = sub('_.*', '', dt1$id)
  if (length(unique(dt1$method))<6){next}
  use.list = c(use.list, ID.tmp)
  write.csv(dt1, paste0('StepCount/xinkai_day_stepcount/', ID, '.csv'))
}

ID.left.2 = setdiff(file.tmp,use.list)
```


## Combine Data Count (Sunan)
```{r}
folder_path = 'StepCount/sunan_day_stepcount/'
files = list.files(folder_path)
result.sunan = data.frame(subjectid = NA,
                    adept = NA,
                    oak = NA,
                    sdt = NA,
                    stepcount = NA,
                    vs = NA)

miss.PAsum.list = c()
ID_list = as.numeric(sub("^[A-Za-z]*", "", dat_PA_m.raw$subjectid))
for (file_name in files){
  file_path = paste0(c(folder_path, file_name), collapse = '')
  dat = read.csv(file_path)
  temp = dat_PA_m.raw[ID_list == unique(dat$id),c(1:4)] |> filter(valid == 1)
  if(sum(ID_list == unique(dat$id)) == 0){miss.PAsum.list = c(miss.PAsum.list, unique(dat$id)); next}
  avg_step = dat[dat$date %in% temp$date,] |> 
    group_by(method) |>
    summarise(mean = mean(steps))
  
  result.sunan = rbind(result.sunan, c(unique(dat$id),avg_step$mean))
}
result.sunan = result.sunan[-1,]
colnames(result.sunan)[which(colnames(result.sunan) == 'stepcount')] = 'stepcount_ssl'
result.sunan$stepcount_rf = NA
result.sunan = result.sunan[,c(1,order(colnames(result.sunan)[-1])+1)]

head(result.sunan)

## regenerate subject ID
result.sunan$subjectid = dat_PA_m.raw$subjectid[match(result.sunan$subjectid, ID_list)]

```

## Combine Data Count (Xinkai)
```{r}
folder_path = 'StepCount/xinkai_day_stepcount/'
files = list.files(folder_path)
result.xinkai = data.frame(subjectid = NA,
                    adept = NA,
                    oak = NA,
                    sdt = NA,
                    stepcount_rf = NA,
                    stepcount_ssl = NA,
                    vs = NA)
for (file_name in files){
  file_path = paste0(c(folder_path, file_name), collapse = '')
  dat = read.csv(file_path); dat$X = NULL
  
  # ID_list = as.numeric(sub("^[A-Za-z]*", "", dat_PA_m.raw$subjectid))
  ID_list = dat_PA_m.raw$subjectid
  temp = dat_PA_m.raw[ID_list == unique(dat$id),c(1:4)] |> filter(valid == 1)
  if(sum(ID_list == unique(dat$id)) == 0){miss.PAsum.list = c(miss.PAsum.list, unique(dat$id)); next}
  avg_step = dat[dat$date %in% temp$date,] |> 
    group_by(method) |>
    summarise(mean = mean(steps))
  avg_step = avg_step[order(avg_step$method),]
  result.xinkai = rbind(result.xinkai, c(unique(dat$id),avg_step$mean))
}
result.xinkai = result.xinkai[-1,]
```

## Generate final daily step count estimates
```{r}
stepcount.day = rbind(result.xinkai, result.sunan)
stepcount.day[,-1] = lapply(stepcount.day[,-1], as.numeric)
# stepcount.day[stepcount.day$subjectid == 'M181520',] # No valid days
stepcount.day = stepcount.day[!rowSums(is.na(stepcount.day)) >1,] # No valid days, N = 12

## Output final stepcount datasets
write.csv(stepcount.day, '00_Intermediate_output/estimated_stepcounts.csv')
```


# 04-Visulize Step Count
## Distribution
### Exclude extreme values
```{r, warning=FALSE}
result = stepcount.day
result$stepcount_rf = NULL
# Exclude results with extreme values
## Define threshold
result = result[rowSums(result[,c(-1)] > 40000) == 0,] # N=1200


## Define outlier observations (Two-side extreme values)
boxplot(result$adept)

## Quantile Distribution
quantile(result$adept, c(0.01, 0.99))
quantile(result$oak, c(0.01, 0.99))
quantile(result$sdt, c(0.01, 0.99))
quantile(result$stepcount_ssl, c(0.01, 0.99))
quantile(result$vs, c(0.01, 0.99))

var_list = c("adept", "oak", "sdt", "stepcount_ssl", "vs")
ex.list = c()
for (var in var_list){
  exetreme.lower = quantile(result[[var]], c(0.01, 0.99))[1]
  exetreme.upper = quantile(result[[var]], c(0.01, 0.99))[2]
  list.temp = result[result[[var]] > exetreme.upper | result[[var]] < exetreme.lower,]$subjectid
  ex.list = c(ex.list, list.temp)
}
result.noextreme = result[result$subjectid %in% setdiff(result$subjectid, unique(ex.list)),]
```

### Histograms of distributions
```{r}
# result = result.noextreme
# result$adept = scale(result$adept)
# result$oak = scale(result$oak)
# result$sdt = scale(result$sdt)
# result$stepcount_ssl = scale(result$stepcount_ssl)
# result$vs = scale(result$vs)

step_name_list = colnames(result)
nm_test.df = data.frame()
par(mfrow=c(2,2))
for (i in 2:ncol(result)){
  step_name = step_name_list[i]
  
  ## Draw Histograms
  plot = ggplot(result) +
    geom_histogram(aes(x = result[,i])) + 
    custom_theme
  print(plot)
  
  ## Nomal Tets
  nm.test = shapiro.test(result[,i])
  temp = data.frame(Name = step_name,
                    Pvalue = nm.test$p.value)
  nm_test.df = rbind(nm_test.df, temp)
}
print(nm_test.df)


## Sunan(620)
result = result.noextreme[1:566,]
step_name_list = colnames(result)
nm_test.df = data.frame()
par(mfrow=c(2,2))
for (i in 2:ncol(result)){
  step_name = step_name_list[i]
  
  ## Draw Histograms
  plot = ggplot(result) +
    geom_density(aes(x = result[,i])) + 
    custom_theme
  print(plot)
  
  ## Nomal Tets
  nm.test = shapiro.test(result[,i])
  temp = data.frame(Name = step_name,
                    Pvalue = nm.test$p.value)
  nm_test.df = rbind(nm_test.df, temp)
}
print(nm_test.df)

## Xinkai(620)
result = result.noextreme[567:1133,]
step_name_list = colnames(result)
nm_test.df = data.frame()
par(mfrow=c(2,2))
for (i in 2:ncol(result)){
  step_name = step_name_list[i]
  
  ## Draw Histograms
  plot = ggplot(result) +
    geom_density(aes(x = result[,i])) + 
    custom_theme
  print(plot)
  
  ## Nomal Tets
  nm.test = shapiro.test(result[,i])
  temp = data.frame(Name = step_name,
                    Pvalue = nm.test$p.value)
  nm_test.df = rbind(nm_test.df, temp)
}
print(nm_test.df)
```

## Correlation
```{r}
## Correlation Plot
library(corrplot)
M = cor(result[,-1])
M.p = cor.mtest(result[,-1], conf.level = 0.95)$p
pdf('Results/Cor_plot.pdf', width = 4, height = 4)
corrplot(M, p.mat = M.p,
         method = 'circle', type = 'upper', 
         insig='blank',
         addCoef.col ='white', 
         number.cex = 0.8, order = 'AOE', diag=FALSE)
dev.off()

## In-pair drawing plots
library(lattice)
library(GGally)

df = result[,-1]
# 使用xyplot函数来创建图形
# xyplot(adept ~ vs, data=result, main="Lattice 散点图", xlab="Variable 1", ylab="Variable 2")
# splom(~df[, 1:ncol(df)], main="Lattice Scatterplot Matrix")

pdf('Results/pair-wise.pdf', height = 8, width = 8)
p = ggpairs(df, title="Pairwise Plots of Different Step Counts", 
        lower = list(continuous = "smooth",#ggally_smooth()
                     #combo = "facethist", 
                     #discrete = "facetbar", 
                     na ="na"),
        diag = list(continuous = "densityDiag", # 'densityDiag', 'barDiag', 'blankDiag'可选
                    #discrete = "barDiag", # 'barDiag', 'blankDiag'可选 
                    #diag =NULL # 不显示diag部分
                    na = "naDiag"))+
  theme_bw() + 
  theme(
      axis.ticks = element_blank(),
      axis.text = element_text(size = 7),
      axis.title = element_text(size = 12, face = "bold"),
      axis.line = element_line(size = 0.5),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5))

if (requireNamespace("grid", quietly = TRUE)) {
  grid::grid.ls(grid::grid.get("vp_3")) # 找到子视图位置的名字
  for (i in 1:p$nrow) {
    for (j in 1:p$ncol) {
      p[i, j] <- p[i, j] + 
        scale_x_continuous(breaks = function(x) pretty(x, n = 3)) +  # X轴只有3个刻度
        scale_y_continuous(breaks = function(x) pretty(x, n = 3))  # Y轴只有3个刻度
    }
  }
}
print(p)
dev.off()
```

## Association with demographyical variable
### Clean Data
```{r}
dat_cov = dat_cov_p1
#dat_cov$subjectid = as.numeric(sub("^[A-Za-z]*", "", dat_cov$subjectid))
#dat_cov.tmp = gsub("[a-zA-Z]", "", data)
dat_vis = merge(result, dat_cov, by = 'subjectid')
dat_vis$sex <- factor(dat_vis$sex, levels = c("0", "1"), labels = c("Female", "Male"))

var_list = c("adept", "oak", "sdt", "stepcount_ssl", "vs")
colnames(dat_vis)
# for (var in var_list){
#   a = summary(lm(hypertension~get(var)+sex+Age, dat_vis))
#   print(a)
# }
# head(dat_vis)
```

### Associations with Age group by Sex.
```{r}
## Continuous Variable
## To better illustraion, we use exam age calcualted by specific days, increasing the power of plots.
plot_list = list()
# dat_vis$adept = scale(dat_vis$adept)
# dat_vis$oak = scale(dat_vis$oak)
# dat_vis$sdt = scale(dat_vis$sdt)
# dat_vis$stepcount_ssl = scale(dat_vis$stepcount_ssl)
# dat_vis$vs = scale(dat_vis$vs)

for (var in var_list){
  plot = ggplot(dat_vis, aes(x = exam_age, y = .data[[var]], color = as.factor(sex))) + 
    # // 0: Female; 1: Male
    geom_smooth() +
    labs(title = "Distribution of Values by Gender",
         x = "Age",
         y = "Step Counts", # paste0(c("Step Count: ",var), collapse = ''),
         color = "Gender") +
    ggtitle(var) +
    theme_minimal()
    #custom_theme
  plot_list[[var]] = plot
}

pdf('Results/Step_vs_Age_by_Sex.pdf', height = 6, width = 9)
plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount + plot_list$vs + 
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()
```

### Associations with Age group by Race
```{r}
plot_list = list()
dat_vis$race <- factor(dat_vis$race, levels = c("0", "1"), labels = c("White", "Black"))
for (var in var_list){
  plot = ggplot(dat_vis, aes(x = exam_age, y = .data[[var]], color = as.factor(race))) +  # // 0: Female; 1: Male
    geom_smooth() +
    labs(title = "Distribution of Values by Gender",
         x = "Age",
         y = paste0(c("Step Count: ",var), collapse = ''),
         color = "Race") +
    ggtitle(var) +
    theme_minimal()
  plot_list[[var]] = plot
}

pdf('Results/Step_vs_Age_by_Race.pdf', height = 6, width = 9)
plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount + plot_list$vs + 
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()
```

### Associations with Age group by Diabets
```{r}
plot_list = list()
# dat_vis$diabetes <- factor(dat_vis$diabetes, levels = c("0", "1"), labels = c("No", "Yes"))
dat_vis$diabetes = ifelse(is.na(dat_vis$diabetes),0,dat_vis$diabetes)
# table(dat_vis$diabetes)
for (var in var_list){
  plot = ggplot(dat_vis, aes(x = exam_age, y = .data[[var]], color = as.factor(diabetes))) +  # // 0: Female; 1: Male
    geom_smooth() +
    labs(title = "Distribution of Values by Gender",
         x = "Age",
         y = paste0(c("Step Count: ",var), collapse = ''),
         color = "Diabetes") +
    ggtitle(var) +
    theme_minimal()
  plot_list[[var]] = plot
}

pdf('Results/Step_vs_Age_by_diabetes.pdf', height = 6, width = 9)
plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount + plot_list$vs + 
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()
```


### Associations with Age group by Hypertension
```{r}
plot_list = list()
dat_vis$BMI_cat <- factor(dat_vis$BMI_cat, levels = c(1, 2, 3, 4), 
                          labels = c("<=18.5", "18.5~24", "24~28", ">28"))
for (var in var_list){
  plot = ggplot(dat_vis, aes(x = exam_age, y = .data[[var]], color = as.factor(BMI_cat))) +
    geom_smooth() +
    labs(title = "Distribution of Values by Gender",
         x = "Age",
         y = paste0(c("Step Count: ",var), collapse = ''),
         color = "BMI") +
    ggtitle(var) +
    theme_minimal()
  plot_list[[var]] = plot
}

pdf('Results/Step_vs_Age_by_BMI.pdf', height = 6, width = 9)
plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount + plot_list$vs + 
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()
```

# 05.Cross-sectional  with health statues
## Construct V9 Covaraites
```{r}
dat_cov_V9 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V9_derive.dta')
dat_cov_V7 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V7_derive.dta')

dat_cov_V9_select <- dat_cov_V9 |>
  mutate(Age = v9age91,
         lisr_index = lisr_i92) |>
  select(-racegrp91, -drnkr91, -diabts96,
         -v9age91,-sport_index, -lisr_index,
         -systolic91, -diastolic91, -sppb91,  -sprt_i91,
         -v9date91_followupdays, # no cigt92
         -lisr_i92, -gender)# no cesd91 

dat_cov_V7_select <- dat_cov_V7 |>
  mutate(Age = v7age71,
         lisr_index = lisr_i72) |>
  select(-bmi71, -racegrp71, -drnkr71, -diabts74, -diabts76,
         -v7age71, -sport_index, -lisr_index,
         -systolic71, -diastolic71, -sppb71, -cigt72, -sprt_i71,
         -v7date71_followupdays,
         -lisr_i72, -cesd71, -gender)

## No cigrate and ces value in visit 9. These data in V9
dat_cov_V9_select = merge(dat_cov_V9_select, 
                          dat_cov_V7_select[,c('subjectid', 'smoking', 'Depre_CES')], 
                         by = 'subjectid', all.x = TRUE)

plot_missing(dat_cov_V9_select)
colnames(dat_cov_V9_select) = sub('_V9', '', colnames(dat_cov_V9_select))

## Add dementia statues
dat_deme = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/Dementia_MCI_derive_V5678.dta')
dat_deme$cogstatus_V8 = ifelse(is.na(dat_deme$cogstatus_V8),0,dat_deme$cogstatus_V8)
# N: Normal, 0
# M: MCI, 1
# D: Dementia, 2
# U: Unknown, .
dat_cov_V9_select = merge(dat_cov_V9_select, dat_deme[,c('subjectid','cogstatus_V8')], 'subjectid', all.x = TRUE)

## Add Apoe4 covariates
dat_apoe4 = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/Genetics/apoe_new_p.dta')
colnames(dat_apoe4)[1] = 'subjectid'
dat_apoe4$final_apoe = ifelse(grepl('4', dat_apoe4$final_apoe), 'Risk',
                              dat_apoe4$final_apoe)
dat_apoe4$final_apoe = ifelse(grepl('2', dat_apoe4$final_apoe), 'Protect',
                              dat_apoe4$final_apoe)
dat_apoe4$final_apoe = ifelse(grepl('3', dat_apoe4$final_apoe), 'Homo',
                              dat_apoe4$final_apoe)

dat_apoe4$APOE_4 = dat_apoe4$final_apoe = ifelse(dat_apoe4$final_apoe == "", NA,
                                                 dat_apoe4$final_apoe)

dat_cov_V9_select = merge(dat_cov_V9_select, dat_apoe4[,c(1,5)], 'subjectid', all.x = TRUE)

## Add Center, Education, Birth
## Center
dat_center = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
table(dat_center$center)
colnames(dat_center)[1] = 'subjectid'
dat_center = dat_center |> select(subjectid, center)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_center, 'subjectid', all.x = TRUE)

## Education
dat_edu = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/education_V1.dta')
table(dat_edu$elevel02)
colnames(dat_edu)[1] = 'subjectid'
dat_edu = dat_edu |> select(subjectid, elevel02)
dat_edu = dat_edu |>
  mutate(Education = factor(
      elevel02,
      levels = c(1, 2, 3),
      labels = c('Less than high school',
                 'High school, GED certification, or vocational schools',
                 'College, graduate, or professional school')))
dat_cov_V9_select = merge(dat_cov_V9_select, dat_edu, 'subjectid', all.x = TRUE)

## Birth
dat_Birth = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
dat_Birth = dat_Birth |> select(id, birthdat, v1date01) |> mutate(subjectid = id) |> select(-id)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_Birth, 'subjectid', all.x = TRUE)
dat_cov_V9_select = dat_cov_V9_select |> mutate(exam_age = (v1date01 - birthdat + exam_dat)/365.25) |>
  select(-v1date01, -birthdat, -elevel02)
plot_missing(dat_cov_V9_select)
```

```{r}
dat_cov = dat_cov_V9_select
```

## Supplement Health Statues
### HF, MI, Stroke, Parkinson
```{r}
dat_CVD = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/CVD_all.dta')

temp = merge(dat_cov, dat_CVD, 'subjectid', all.x = TRUE)
## Generate HF records
list_HF = temp |>
  mutate(time_label = HF_date <= exam_dat,
         HF_label = ifelse(HF == 1 & time_label, 1,0),
         HF = HF_label) |>
  select(-HF_label, -time_label, -HF_date)
list_HF$HF = ifelse(is.na(list_HF$HF), 0,list_HF$HF)

## Generate MI records
list_MI = temp |>
  mutate(time_label = MI_date <= exam_dat,
         MI_label = ifelse(MI == 1 & time_label, 1,0),
         MI = MI_label) |>
  select(-MI_label, -time_label, -MI_date) # The list of individuals who have HF before V5.
list_MI$MI = ifelse(is.na(list_MI$MI), 0,list_MI$MI)

## Generate Stroke records
list_stroke = temp |>
  mutate(time_label = stroke_date <= exam_dat,
         stroke_label = ifelse(stroke == 1 & time_label, 1,0),
         stroke = stroke_label) |>
  select(-stroke_label, -time_label, -stroke_date) # The list of individuals who have HF before V5.
list_stroke$stroke = ifelse(is.na(list_stroke$stroke), 0,list_stroke$stroke)

sum(!dat_cov$subjectid == list_HF$subjectid)
sum(!dat_cov$subjectid == list_MI$subjectid)
sum(!dat_cov$subjectid == list_stroke$subjectid)

dat_cov$HF = list_HF$HF
dat_cov$MI = list_MI$MI
dat_cov$Stroke = list_stroke$stroke


## Generate Parkinson disease
dat_Parkinson = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/Parkison_all.dta')

temp = merge(dat_cov, dat_Parkinson, 'subjectid', all.x = TRUE)
list_Parkison = temp |>
  mutate(time_label = Parkison_date <= exam_dat,
         Parkison_label = ifelse(Parkison == 'Y' & time_label, 1,0),
         Parkison = Parkison_label) |>
  select(-Parkison_label, -time_label, -Parkison_date)
list_Parkison$Parkison = ifelse(is.na(list_Parkison$Parkison), 0,list_Parkison$Parkison)
sum(!dat_cov$subjectid == list_Parkison$subjectid)
dat_cov$Parkison = list_Parkison$Parkison
plot_missing(dat_cov)
```

### PA-related outcome
Frality
```{r}

```

## Association results
### Define Types
```{r}
colnames(dat_cov)
dat_cov$APOE_4 = as.factor(dat_cov$APOE_4)
dat_cov$cogstatus = as.factor(dat_cov$cogstatus)
dat_cov$smoking = as.factor(dat_cov$smoking)
dat_cov$drinking = as.factor(dat_cov$drinking)
dat_cov$diabetes = as.factor(dat_cov$diabetes)
dat_cov$hypertension = as.factor(dat_cov$hypertension)
dat_cov$BMI_cat = as.factor(dat_cov$BMI_cat)
dat_cov$race = as.factor(dat_cov$race)
dat_cov$sex = as.factor(dat_cov$sex)
dat_cov$Education = as.factor(dat_cov$Education)
dat_cov$HF = as.factor(dat_cov$HF)
dat_cov$MI = as.factor(dat_cov$MI)
dat_cov$Stroke = as.factor(dat_cov$Stroke)
dat_cov$Parkison = as.factor(dat_cov$Parkison)

dat_cov$APOE_4 = ifelse(dat_cov$APOE_4 %in% c('Homo', 'Protect'), 
                        'No ε4 allele', '≥1 APOE ε4 allelel')
table(dat_cov$APOE_4)
```

### Define Covariate types
```{r}
## SPPB
dt = dat_cov

## Co-variables
dt = dt %>%
  filter(race %in% c('0','1')) %>%
  mutate(
    Age = Age,
    `Heart failure` = HF,
    `Myocardial infarction` = MI,
    Sex = factor(
           sex,
           levels = c("0", "1"),
           labels = c("Female", "Male")))  %>%
  mutate(
    Race = factor(
      race,
      levels = c("0", "1"),
      labels = c("White", "Black")
    ),
    BMI = factor(
      BMI_cat,
      levels = c("1", "2", "3", "4"),
      labels = c("<=18.5", "18.5~24.9", "25~29.9", ">=30")
    ),
    Hypertension = factor(
      hypertension,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Diabetes = factor(
      diabetes,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Parkison = factor(
      Parkison,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Stroke = factor(
      Stroke,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Heart_failure = factor(
      `Heart failure`,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Myocardial_infarction = factor(
      `Myocardial infarction`,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    )
  )  %>%
  mutate(SPPB = sppb_score,
         Center = center,
         CES_D = Depre_CES) %>%
  mutate(APOE = factor(
      APOE_4,
      levels = c('No ε4 allele', '≥1 APOE ε4 allelel')),
      Education = factor(Education, 
                         levels = c('Less than high school',
                           'High school, GED certification, or vocational schools',
                           'College, graduate, or professional school'),
                         labels = c('Basic Education', 
                                               'Intermediate Education',
                                               'Advanced Education')),
      Smoking = factor(
        smoking,
        levels = c(1,2,3),
        labels = c('Current smoker',
                   'Former smoker',
                   'Never smoker')
      ),
      Drinking = factor(
        drinking,
        levels = c(1,2,3),
        labels = c('Current drinker',
                   'Former drinker',
                   'Never drinker')
      ),
      Center = factor(
        Center,
        levels = c('F', 'J', 'M', 'W'),
        labels = c('Forsyth County, NC',
                   'Jackson, MS',
                   'Minneapolis, MN',
                   'Washington County, MD')
      ))

dt = dt |>
  select(-sex, -race, -hypertension, -diabetes, -drinking,
         -smoking, -sppb_score, -HF, -MI)


dt = dt |> 
  mutate(BMI_cat = case_when(
    BMI_cat == '1' | BMI_cat == '2' ~ '1',
    BMI_cat == '3' ~ '2',
    BMI_cat == '4' ~ '3',
  )) |>
  mutate(BMI = factor(
      BMI_cat,
      levels = c("1", "2", "3"),
      labels = c("<=24.9", "25~29.9", ">=30")
    ))
```

```{r}
cov_all = colnames(dt)
cov_demo = c(which(cov_all == 'Age'),
             which(cov_all == 'Sex'),
             which(cov_all == 'Race'),
             which(cov_all == 'Education'),
             which(cov_all == 'Center'))
cov_life_gen = c(which(cov_all == 'Smoking'),
                 which(cov_all == 'Drinking'),
                 which(cov_all == 'BMI'))
# cov_health_bio = c(which(cov_all == 'CES-D'),
#                    which(cov_all == 'Hypertension'),
#                    which(cov_all == 'Diabetes'),
#                    which(cov_all == 'Multimorbidity'),
#                  which(cov_all == 'TC'),
#                  which(cov_all == 'TG'),
#                  which(cov_all == 'HDL'),
#                  which(cov_all == 'LDL'),
#                  which(cov_all == 'eGFR'))
# cov_physical = c(which(cov_all == 'SPPB'),
#                  which(cov_all == 'Sports participation'))
```

### Merge final data
```{r}
dt.all = merge(result.noextreme, dt, by = 'subjectid')
```

## Check Associations
1. Metabolic outcome: body mass index (BMI), waist circumference, triglyceride (TG), total cholesterol (TC), high-density lipoprotein cholesterol (HDL-C) and low-density lipoprotein cholesterol (LDL-C), type 2 diabetes
2. Cardiovascular diseases: heart failure, myocardial infarction, stroke, systolic blood pressure (SBP), diastolic blood pressure (DBP), carotid-femoral pulse wave velocity (cfPWV)
3. Other health statues: falls, fear of falling, frailty, global and domain-specific cognitive function, and depression.

### Continuous
```{r}
colnames(dt.all)
out.list.continuous = c('CES_D', "bmi91")

continuous_model_list <- list()
continuous.result = list()


for (out in out.list.continuous){
  column_names = c('Estimate', 'SE', 'T_value', 'P_value')
  matrix = matrix(NA * length(var_list)*length(column_names), 
                  nrow = length(var_list), 
                  ncol = length(column_names))
  df <- data.frame(matrix)
  colnames(df) <- column_names
  rownames(df) <- var_list
  
  for (step_var in var_list){
    comb = paste0(c(out, '&', step_var), collapse = '')
    formula.tmp = as.formula(paste0(out,'~',step_var,'+',
                                    paste0(c(cov_all[c(cov_demo)]), # , cov_life_gen
                                         collapse = '+')))
    continuous_model_list[[comb]] = lm(formula.tmp, dt.all)
    result.tmp = summary(continuous_model_list[[comb]])$coefficients
    df[step_var,] = result.tmp[2,]
  }
  continuous.result[[out]] = df
}

continuous.result$CES_D
continuous.result$bmi91
```

### Binary
```{r}
out.list.binary = c('Hypertension','Stroke', 'Parkison',
        'Heart_failure', 'Myocardial_infarction',
        'Diabetes')

binary_model_list <- list()
binary.result = list()


dt.all$adept = scale(dt.all$adept)
dt.all$oak = scale(dt.all$oak)
dt.all$sdt = scale(dt.all$sdt)
dt.all$stepcount_ssl = scale(dt.all$stepcount_ssl)
dt.all$vs = scale(dt.all$vs)


for (out in out.list.binary){
  column_names = c('Estimate', 'SE', 'T_value', 'P_value')
  matrix = matrix(NA * length(var_list)*length(column_names), 
                  nrow = length(var_list), 
                  ncol = length(column_names))
  df <- data.frame(matrix)
  colnames(df) <- column_names
  rownames(df) <- var_list
  
  for (step_var in var_list){
    comb = paste0(c(out, '&', step_var), collapse = '')
    formula.tmp = as.formula(paste0(out,'~',step_var,'+',
                                    paste0(c(cov_all[c(cov_demo)]), # , cov_life_gen
                                         collapse = '+')))
    binary_model_list[[comb]] = glm(formula.tmp, dt.all, family = binomial)
    result.tmp = summary(binary_model_list[[comb]])$coefficients
    df[step_var,] = result.tmp[2,]
  }
  binary.result[[out]] = df
}
binary.result$Hypertension
binary.result$Stroke
binary.result$Parkison
binary.result$Diabetes
binary.result$Heart_failure
binary.result$Myocardial_infarction
  ## All share the same directions of associations

out.list.binary = c('Hypertension','Stroke', 'Parkison',
        'Heart_failure', 'Myocardial_infarction',
        'Diabetes')
```


