---
title: "01_Description_Analysis"
---
# Set Parameters and Load Packages
```{r}
library(readr)
library(haven)
library(dplyr)
library(ggplot2)
library(DataExplorer)
library(patchwork)

custom_theme <- theme(
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  axis.text = element_text(size = 10),
  axis.title = element_text(size = 12, face = "bold"),
  axis.line = element_line(size = 0.5),
  plot.title = element_text(size = 14, face = "bold", hjust = 0.5)
)

custom_theme2 <- theme(
    panel.grid.major = element_blank(),  
    panel.grid.minor = element_blank(),  
    panel.background = element_blank(),  
    axis.ticks = element_blank(),  
    panel.border = element_rect(colour = "black", fill = NA, size = 1)
  )

step_algorithms = c('ADEPT', 'OAK', 'SDT', 'Stepcount', 'Verisense')
```

# 01.Visualize Step Counts
## Load data
```{r}
result = read_csv('00_Intermediate_output/estimated_stepcounts.csv'); result$...1 = NULL
result$stepcount_rf = NULL # exclude generated value from random forest
```

## Exclude extreme values
### by 0.01 and 0.99 limits
```{r, warning=FALSE}
var_list = c("adept", "oak", "sdt", "stepcount_ssl", "vs")
ex.list = c()
for (var in var_list){
  exetreme.lower = quantile(result[[var]], c(0.01, 0.99))[1]
  exetreme.upper = quantile(result[[var]], c(0.01, 0.99))[2]
  list.temp = result[result[[var]] > exetreme.upper | result[[var]] < exetreme.lower,]$subjectid
  ex.list = c(ex.list, list.temp)
}
result.noextreme = result[result$subjectid %in% setdiff(result$subjectid, unique(ex.list)),] # N=62 excluded
cat('The number of individuals who are excluded due to extreme values: ', dim(result)[1] - dim(result.noextreme)[1])
```

### by Adaptive Trimmed Mean Estimator
```{r}
# install.packages("robustbase")
library(robustbase)
adjbox_result <- adjbox(result$vs, id.n = Inf, plot = TRUE)
list = which(result$adept  %in%  adjbox_result$out) # obtain outlier data

var_list = c("adept", "oak", "sdt", "stepcount_ssl", "vs")
ex.list = c()
for (var in var_list){
  adjbox_result <- adjbox(result[[var]], id.n = Inf, plot = TRUE)
  list.temp = which(result[[var]]  %in%  adjbox_result$out)
  ex.list = c(ex.list, list.temp)
}
ex.list = result$subjectid[ex.list]

result.noextreme = result[result$subjectid %in% setdiff(result$subjectid, unique(ex.list)),] # N=62 excluded
cat('The number of individuals who are excluded due to extreme values: ', dim(result)[1] - dim(result.noextreme)[1])
```

## Distributions of step counts
### Density Plots
```{r}
nm_test.df = data.frame()
plt.list = list()

for (i in 2:ncol(result)){
  step_name = colnames(result.noextreme)[i]
  
  ## Draw Histograms
  plot = ggplot(result.noextreme) +
    #geom_histogram(aes(x = .data[[step_name]])) + 
    geom_density(aes(x = .data[[step_name]]))+
    custom_theme + 
    labs(x = "Step counts per day", y = 'Counts',
         title = step_algorithms[i-1]) + 
    scale_y_continuous(labels = scales::scientific_format(digits = 1))
    
  plt.list[[step_name]] = plot
  
  ## Nomal Tets
  nm.test = shapiro.test(result.noextreme[[step_name]])
  temp = data.frame(Name = step_name,
                    Pvalue = nm.test$p.value)
  nm_test.df = rbind(nm_test.df, temp)
}

pdf('Results/01_Density_plots.pdf', height = 6, width = 8)
plt.list$adept + plt.list$oak + plt.list$sdt + plt.list$stepcount_ssl + plt.list$vs
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()

# print(nm_test.df)
```

Question: Do we need to make the X-axis the same scale in all algorithms

### Histogram Plots
```{r}
nm_test.df = data.frame()
plt.list = list()

for (i in 2:ncol(result)){
  step_name = colnames(result.noextreme)[i]
  
  ## Draw Histograms
  plot = ggplot(result.noextreme) +
    geom_histogram(aes(x = .data[[step_name]])) + 
    custom_theme + 
    labs(x = "Step counts per day", y = 'Counts',
         title = step_algorithms[i-1])
    #scale_x_continuous(limits = c(0, 50000))
    #scale_y_continuous(labels = scales::scientific_format(digits = 1))
    
  plt.list[[step_name]] = plot
}

pdf('Results/01_Histograms_plots.pdf', height = 6, width = 8)
plt.list$adept + plt.list$oak + plt.list$sdt + plt.list$stepcount_ssl + plt.list$vs
  plot_layout(guides = "collect") &
  theme(legend.position = 'bottom')
dev.off()
```

## Scatter Plots and Correlation
### Scatter Plots
```{r}
library(lattice)
library(GGally)
dat = result.noextreme

df = dat[,-1]
pdf('Results/02_Scatter_Corr.pdf', height = 8, width = 8)
p = ggpairs(df, title="Pairwise Plots of Different Step Counts", 
        lower = list(continuous = "smooth",#ggally_smooth()
                     #combo = "facethist", 
                     #discrete = "facetbar", 
                     na ="na"),
        diag = list(continuous = "densityDiag", # 'densityDiag', 'barDiag', 'blankDiag'可选
                    #discrete = "barDiag", # 'barDiag', 'blankDiag'可选 
                    #diag =NULL # 不显示diag部分
                    na = "naDiag"))+
  theme_bw() + 
  theme(
      axis.ticks = element_blank(),
      axis.text = element_text(size = 7),
      axis.title = element_text(size = 12, face = "bold"),
      axis.line = element_line(size = 0.5),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5))

if (requireNamespace("grid", quietly = TRUE)) {
  grid::grid.ls(grid::grid.get("vp_3")) # 找到子视图位置的名字
  for (i in 1:p$nrow) {
    for (j in 1:p$ncol) {
      p[i, j] <- p[i, j] + 
        scale_x_continuous(breaks = function(x) pretty(x, n = 3)) +  # X轴只有3个刻度
        scale_y_continuous(breaks = function(x) pretty(x, n = 3))  # Y轴只有3个刻度
    }
  }
}
print(p)
dev.off()
```

### Data Correlations
```{r}
## Correlation Plot
dat = result.noextreme
library(corrplot)
M = cor(dat[,-1])
colnames(M) = step_algorithms
rownames(M) = step_algorithms
M.p = cor.mtest(dat[,-1], conf.level = 0.95)$p
pdf('Results/02_Correlation.pdf', width = 4, height = 4)
corrplot(M, p.mat = M.p,
         method = 'circle', type = 'upper', 
         insig='blank',
         addCoef.col ='white', 
         number.cex = 0.8, order = 'AOE', diag=FALSE)
dev.off()
```

### Distribution Correlations (KS)
Kolmogorov-Smirnov test
```{r, warning=FALSE}
algorithms = colnames(result.noextreme)[-1]
data = result.noextreme
# data[,-1] = scale(data[,-1])
ks_tests <- matrix(NA, nrow = length(algorithms), ncol = length(algorithms), dimnames = list(algorithms, algorithms))

for (i in 1:length(algorithms)) {
  for (j in 1:length(algorithms)) {
    if (i < j) {
      ks_test <- ks.test(data[[algorithms[i]]], data[[algorithms[j]]])
      ks_tests[i, j] <- ks_test$p.value
    }
  }
}

ks_tests
```

## Agreement Analysis
### Bland-Altman analysis
```{r}
library(blandr)
library(gridExtra)
library(patchwork)

# blandr.draw(result.noextreme$adept, result.noextreme$oak)
# blandr.statistics(result.noextreme$adept, result.noextreme$oak)
# blandr.draw(result.noextreme$adept, result.noextreme$oak) + custom_theme

# Generate all Bland-Altman plots
bland_altman_plots <- list()
algorithms = colnames(result.noextreme)[-1]
for (i in 1:(length(algorithms) - 1)) {
  for (j in (i+1):length(algorithms)) {
    bland_altman_plots[[paste(algorithms[i], algorithms[j], sep = "_vs_")]] <- 
      blandr.draw(result.noextreme[[algorithms[i]]], result.noextreme[[algorithms[j]]]) + 
      custom_theme + 
      labs(#x = "Step counts per day", y = 'Counts',
         title = paste0(step_algorithms[i],' - ', step_algorithms[j]))
      
  }
}
plot.null = ggplot() + geom_blank() + custom_theme


combined_plot <- wrap_plots(
  #bland_altman_plots$adept_vs_adept,
  bland_altman_plots$adept_vs_oak,
  bland_altman_plots$adept_vs_sdt,
  bland_altman_plots$adept_vs_stepcount_ssl,
  bland_altman_plots$adept_vs_vs,
  plot.null,
  #bland_altman_plots$oak_vs_oak,
  bland_altman_plots$oak_vs_sdt,
  bland_altman_plots$oak_vs_stepcount_ssl,
  bland_altman_plots$oak_vs_vs,
  plot.null,
  plot.null,
  #bland_altman_plots$sdt_vs_sdt,
  bland_altman_plots$sdt_vs_stepcount_ssl,
  bland_altman_plots$sdt_vs_vs,
  plot.null,
  plot.null,
  plot.null,
  #bland_altman_plots$stepcount_ssl_vs_stepcount_ssl,
  bland_altman_plots$stepcount_ssl_vs_vs,
  ncol = 4
) & 
theme(legend.position = 'bottom')

pdf('Results/03_Bland-Altman.pdf', width = 14, height = 14)
print(combined_plot)
dev.off()
```

### Bland-Altman analysis (Scaled)
```{r}
library(blandr)
library(gridExtra)
library(patchwork)

data = result.noextreme
data[,-1] = scale(data[,-1])
# Generate all Bland-Altman plots
bland_altman_plots <- list()
algorithms = colnames(data)[-1]
for (i in 1:(length(algorithms) - 1)) {
  for (j in (i+1):length(algorithms)) {
    bland_altman_plots[[paste(algorithms[i], algorithms[j], sep = "_vs_")]] <- 
      blandr.draw(data[[algorithms[i]]], data[[algorithms[j]]]) + 
      custom_theme + 
      labs(#x = "Step counts per day", y = 'Counts',
         title = paste0(step_algorithms[i],' - ', step_algorithms[j]))
      
  }
}
plot.null = ggplot() + geom_blank() + custom_theme


combined_plot <- wrap_plots(
  #bland_altman_plots$adept_vs_adept,
  bland_altman_plots$adept_vs_oak,
  bland_altman_plots$adept_vs_sdt,
  bland_altman_plots$adept_vs_stepcount_ssl,
  bland_altman_plots$adept_vs_vs,
  plot.null,
  #bland_altman_plots$oak_vs_oak,
  bland_altman_plots$oak_vs_sdt,
  bland_altman_plots$oak_vs_stepcount_ssl,
  bland_altman_plots$oak_vs_vs,
  plot.null,
  plot.null,
  #bland_altman_plots$sdt_vs_sdt,
  bland_altman_plots$sdt_vs_stepcount_ssl,
  bland_altman_plots$sdt_vs_vs,
  plot.null,
  plot.null,
  plot.null,
  #bland_altman_plots$stepcount_ssl_vs_stepcount_ssl,
  bland_altman_plots$stepcount_ssl_vs_vs,
  ncol = 4
) & 
theme(legend.position = 'bottom')

pdf('Results/03_Bland-Altman_scaled.pdf', width = 14, height = 14)
print(combined_plot)
dev.off()
```

# 02. Generate Co-variate datasets
## V5-V9 Covaraites
```{r}
dat_cov_V5 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V5_derive.dta')
dat_cov_V6 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V6_derive.dta')
dat_cov_V7 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V7_derive.dta')
dat_cov_V9 = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/covariate_V9_derive.dta')

dat_cov_V5_select <- dat_cov_V5 |>
  mutate(Age = v5age51) |>
  select(-bmi51, -racegrp51, -drnkr51, -diabts54, -diabts56,
         -v5age51,
         -systolic51, -diastolic51, -sppb51, -cigt52, -sprt_i51,
         -lisr_i52, -cesd51, -gender, -v5date51_followupdays)
  
  # sex // 0: Female; 1: Male

dat_cov_V6_select <- dat_cov_V6 |>
  mutate(Age = v6age61) |>
  select(-bmi61, -racegrp61, -drnkr61, -diabts64, -diabts66,
         -v6age61,
         -systolic61, -diastolic61, -sppb61, -cigt62, -sprt_i61,
         -v6date61_followupdays,
         -lisr_i62, -cesd61, -gender)
  

dat_cov_V7_select <- dat_cov_V7 |>
  mutate(Age = v7age71) |>
  select(-bmi71, -racegrp71, -drnkr71, -diabts74, -diabts76,
         -v7age71,
         -systolic71, -diastolic71, -sppb71, -cigt72, -sprt_i71,
         -v7date71_followupdays,
         -lisr_i72, -cesd71, -gender)
  

dat_cov_V9_select <- dat_cov_V9 |>
  mutate(Age = v9age91) |>
  select(-bmi91, -racegrp91, -drnkr91, -diabts96,
         -v9age91,
         -systolic91, -diastolic91, -sppb91,  -sprt_i91,
         -v9date91_followupdays, # no cigt92
         -lisr_i92, -gender)# no cesd91 


## No cigrate and ces value in visit 9. These data in V9
dat_cov_V9_select = merge(dat_cov_V9_select, 
                          dat_cov_V7_select[,c('subjectid', 'smoking', 'Depre_CES')], 
                         by = 'subjectid', all.x = TRUE)

dat_cov_V9_select = dat_cov_V9_select[, c(1:7, 13, 8, 12, 9:11)] # match each column name in visits


## Add dementia statues
dat_deme = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/Dementia_MCI_derive_V5678.dta')
dat_deme$cogstatus_V5 = ifelse(dat_deme$cogstatus_V5>=1,1,0)
dat_deme$cogstatus_V6 = ifelse(dat_deme$cogstatus_V6>=1,1,0)
dat_deme$cogstatus_V7 = ifelse(dat_deme$cogstatus_V7>=1,1,0)
dat_deme$cogstatus_V8 = ifelse(dat_deme$cogstatus_V8>=1,1,0)
# N: Normal, 0
# M: MCI, 1
# D: Dementia, 2
# U: Unknown, .

dat_cov_V5_select = merge(dat_cov_V5_select, dat_deme[,c('subjectid','cogstatus_V5')], 'subjectid', all.x = TRUE)
dat_cov_V6_select = merge(dat_cov_V6_select, dat_deme[,c('subjectid','cogstatus_V6')], 'subjectid', all.x = TRUE)
dat_cov_V7_select = merge(dat_cov_V7_select, dat_deme[,c('subjectid','cogstatus_V7')], 'subjectid', all.x = TRUE)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_deme[,c('subjectid','cogstatus_V8')], 'subjectid', all.x = TRUE)


## Add Apoe4 covariates
dat_apoe4 = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/Genetics/apoe_new_p.dta')
colnames(dat_apoe4)[1] = 'subjectid'
dat_apoe4$final_apoe = ifelse(grepl('4', dat_apoe4$final_apoe), 'Risk',
                              dat_apoe4$final_apoe)
dat_apoe4$final_apoe = ifelse(grepl('2', dat_apoe4$final_apoe), 'Protect',
                              dat_apoe4$final_apoe)
dat_apoe4$final_apoe = ifelse(grepl('3', dat_apoe4$final_apoe), 'Homo',
                              dat_apoe4$final_apoe)

dat_apoe4$APOE_4 = dat_apoe4$final_apoe = ifelse(dat_apoe4$final_apoe == "", NA, dat_apoe4$final_apoe)

dat_cov_V5_select = merge(dat_cov_V5_select, dat_apoe4[,c(1,5)], 'subjectid', all.x = TRUE)
dat_cov_V6_select = merge(dat_cov_V6_select, dat_apoe4[,c(1,5)], 'subjectid', all.x = TRUE)
dat_cov_V7_select = merge(dat_cov_V7_select, dat_apoe4[,c(1,5)], 'subjectid', all.x = TRUE)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_apoe4[,c(1,5)], 'subjectid', all.x = TRUE)



## Add Center, Education, Birth
## Center
dat_center = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
table(dat_center$center)
colnames(dat_center)[1] = 'subjectid'
dat_center = dat_center |> select(subjectid, center)

dat_cov_V5_select = merge(dat_cov_V5_select, dat_center, 'subjectid', all.x = TRUE)
dat_cov_V6_select = merge(dat_cov_V6_select, dat_center, 'subjectid', all.x = TRUE)
dat_cov_V7_select = merge(dat_cov_V7_select, dat_center, 'subjectid', all.x = TRUE)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_center, 'subjectid', all.x = TRUE)


## Education
dat_edu = read_dta('/Users/gsn/Library/CloudStorage/OneDrive-JohnsHopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/education_V1.dta')
table(dat_edu$elevel02)
colnames(dat_edu)[1] = 'subjectid'
dat_edu = dat_edu |> select(subjectid, elevel02)
dat_edu = dat_edu |>
  mutate(Education = factor(
      elevel02,
      levels = c(1, 2, 3),
      labels = c('Less than high school',
                 'High school, GED certification, or vocational schools',
                 'College, graduate, or professional school')))

dat_cov_V5_select = merge(dat_cov_V5_select, dat_edu, 'subjectid', all.x = TRUE)
dat_cov_V6_select = merge(dat_cov_V6_select, dat_edu, 'subjectid', all.x = TRUE)
dat_cov_V7_select = merge(dat_cov_V7_select, dat_edu, 'subjectid', all.x = TRUE)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_edu, 'subjectid', all.x = TRUE)


## Birth
dat_Birth = read_dta('/Users/gsn/OneDrive - Johns Hopkins/ARIC_Data/Data/ARIC/V1/derive13.dta')
dat_Birth = dat_Birth |> select(id, birthdat, v1date01) |> mutate(subjectid = id) |> select(-id)
dat_cov_V5_select = merge(dat_cov_V5_select, dat_Birth, 'subjectid', all.x = TRUE)
dat_cov_V6_select = merge(dat_cov_V6_select, dat_Birth, 'subjectid', all.x = TRUE)
dat_cov_V7_select = merge(dat_cov_V7_select, dat_Birth, 'subjectid', all.x = TRUE)
dat_cov_V9_select = merge(dat_cov_V9_select, dat_Birth, 'subjectid', all.x = TRUE)

## Label data into different visits
dat_cov_V5_select$Visit = 'V5'
dat_cov_V6_select$Visit = 'V6'
dat_cov_V7_select$Visit = 'V7'
dat_cov_V9_select$Visit = 'V9'
```

### Combine together
```{r}
colnames(dat_cov_V5_select) = sub('_V.', '', colnames(dat_cov_V5_select))
colnames(dat_cov_V6_select) = sub('_V.', '', colnames(dat_cov_V6_select))
colnames(dat_cov_V7_select) = sub('_V.', '', colnames(dat_cov_V7_select))
colnames(dat_cov_V9_select) = sub('_V.', '', colnames(dat_cov_V9_select))
dat_all = rbind(dat_cov_V5_select, 
                rbind(dat_cov_V6_select,
                      rbind(dat_cov_V7_select, dat_cov_V9_select)))
```

### Supplement Covariates
If covariates at visit 9 are missing, measurements in prior visits will be considered
```{r}
df_grouped <- split(dat_all, dat_all$subjectid)

for (i in 1:length(df_grouped)) {
  subject_data <- df_grouped[[i]]
  if (dim(subject_data)[1] <= 1){next}
  
  # Process for each variable
  ## The number where the co-variable begins
  num_cov = which(colnames(subject_data) == 'sex')
  for (j in num_cov:ncol(subject_data)) {
    var <- subject_data[, j]
    missing_values <- is.na(var) # find the missing values
    
    # 如果当前变量缺失值，且不是第一个观测，则用前一个观测的值填充
    for (k in 2:length(var)) {
      if (missing_values[k] && !missing_values[k - 1]) {
        var[k] <- var[k - 1]
      }
    }
    
    subject_data[, j] <- var
  }
  
  df_grouped[[i]] <- subject_data
}

# combine processed data
df_filled <- do.call(rbind, df_grouped)

plot_missing(df_filled[df_filled$Visit == 'V9',])
plot_missing(dat_cov_V9_select)

dat_V9_final = df_filled[df_filled$Visit == 'V9',]
# write.csv(dat_V9_final, '00_Intermediate_output/Cov_dat_V9.csv')
```

## Define Variable Types
```{r}
colnames(dat_V9_final)
dat_V9_final$APOE_4 = as.factor(dat_V9_final$APOE_4)
dat_V9_final$cogstatus = as.factor(dat_V9_final$cogstatus)
dat_V9_final$smoking = as.factor(dat_V9_final$smoking)
dat_V9_final$drinking = as.factor(dat_V9_final$drinking)
dat_V9_final$diabetes = as.factor(dat_V9_final$diabetes)
dat_V9_final$hypertension = as.factor(dat_V9_final$hypertension)
dat_V9_final$BMI_cat = as.factor(dat_V9_final$BMI_cat)
dat_V9_final$race = as.factor(dat_V9_final$race)
dat_V9_final$sex = as.factor(dat_V9_final$sex)
dat_V9_final$Education = as.factor(dat_V9_final$Education)
# dat_V9_final$HF = as.factor(dat_V9_final$HF)
# dat_V9_final$MI = as.factor(dat_V9_final$MI)
# dat_V9_final$stroke = as.factor(dat_V9_final$stroke)

dat_V9_final$APOE_4 = ifelse(dat_V9_final$APOE_4 %in% c('Homo', 'Protect'), 'No ε4 allele', '≥1 APOE ε4 allelel')
table(dat_V9_final$APOE_4)
```

## Define Variable Name
```{r}
## SPPB
dat.table = dat_V9_final

## Co-variables
dat.table <- dat.table %>%
  filter(race %in% c('0','1')) %>%
  mutate(
    Age = Age,
    `Sports participation` = sport_index,
    # `Heart failure` = HF,
    # `Myocardial infarction` = MI,
    Sex = factor(
           sex,
           levels = c("0", "1"),
           labels = c("Female", "Male")))  %>%
  mutate(
    Race = factor(
      race,
      levels = c("0", "1"),
      labels = c("White", "Black")
    ),
    BMI = factor(
      BMI_cat,
      levels = c("1", "2", "3", "4"),
      labels = c("<=18.5", "18.5~24.9", "25~29.9", ">=30")
    ),
    Hypertension = factor(
      hypertension,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    Diabetes = factor(
      diabetes,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    cogstatus = factor(
      cogstatus,
      levels = c("0", "1"),
      labels = c("No", "Yes")
    ),
    # Parkison = factor(
    #   Parkison,
    #   levels = c("0", "1"),
    #   labels = c("No", "Yes")
    # ),
    # Stroke = factor(
    #   stroke,
    #   levels = c("0", "1"),
    #   labels = c("No", "Yes")
    # ),
    # `Heart failure` = factor(
    #   `Heart failure`,
    #   levels = c("0", "1"),
    #   labels = c("No", "Yes")
    # ),
    # `Myocardial infarction` = factor(
    #   `Myocardial infarction`,
    #   levels = c("0", "1"),
    #   labels = c("No", "Yes")
    # )
  )  %>%
  mutate(SPPB = sppb_score,
         Center = center,
         `CES-D` = Depre_CES) %>%
  mutate(APOE = factor(
      APOE_4,
      levels = c('No ε4 allele', '≥1 APOE ε4 allelel')),
      Education = factor(Education, 
                         levels = c('Less than high school',
                           'High school, GED certification, or vocational schools',
                           'College, graduate, or professional school'),
                         labels = c('Basic Education', 
                                               'Intermediate Education',
                                               'Advanced Education')),
      Smoking = factor(
        smoking,
        levels = c(1,2,3),
        labels = c('Current smoker',
                   'Former smoker',
                   'Never smoker')
      ),
      Drinking = factor(
        drinking,
        levels = c(1,2,3),
        labels = c('Current drinker',
                   'Former drinker',
                   'Never drinker')
      ),
      Center = factor(
        Center,
        levels = c('F', 'J', 'M', 'W'),
        labels = c('Forsyth County, NC',
                   'Jackson, MS',
                   'Minneapolis, MN',
                   'Washington County, MD')
      ))

colnames(dat.table)
dat.table = dat.table |>
  select(-sex, -race, -hypertension, -diabetes, -drinking,
         -smoking, -sppb_score)


dat.table = dat.table |> 
  mutate(BMI_cat = case_when(
    BMI_cat == '1' | BMI_cat == '2' ~ '1',
    BMI_cat == '3' ~ '2',
    BMI_cat == '4' ~ '3',
  )) |>
  mutate(BMI = factor(
      BMI_cat,
      levels = c("1", "2", "3"),
      labels = c("<=24.9", "25~29.9", ">=30")
    ))

# write.csv(dat.table, '00_Intermediate_output/Cov_dat_V9_2.csv')
```



# 03.Association with demographyical variable
## Load and merge data
```{r}
dat_1 = read.csv('00_Intermediate_output/Cov_dat_V9.csv'); dat_V9_cov$X = NULL
dat_2 = read.csv('00_Intermediate_output/Cov_dat_V9_2.csv'); dat_V9_cov$X = NULL

# Differences in the race
```


```{r}
dat_V9_cov = read.csv('00_Intermediate_output/Cov_dat_V9_2.csv'); dat_V9_cov$X = NULL
dat_vis = merge(result.noextreme, dat_V9_cov, by = 'subjectid', all.x = TRUE)
dat_vis = merge(result.noextreme, dat_V9_cov, by = 'subjectid') # N=1168 (Steps in total: 1203)
sum(is.na(dat_vis$sex)) # N=40

# setwd('/Users/gsn/OneDrive - Johns Hopkins/【JHU】Aging-RA/EBA_Cog_PA/Derived_Data/')
# dat_cov_V9 = read_dta('covariate_V9_derive.dta')
# dat.vis.2 = merge(result.noextreme, df_filled, by = 'subjectid', all.x = TRUE)
# 
# plot_missing(dat.vis)
# plot_missing(dat.vis.2)
# dat.vis[is.na(dat.vis$sex),]
# dat.vis.2[is.na(dat.vis.2$sex),]

step_algorithms = c('ADEPT', 'OAK', 'SDT', 'Stepcount', 'Verisense')
dat_vis$v1date01 = as.Date(dat_vis$v1date01)
dat_vis$birthdat = as.Date(dat_vis$birthdat)
dat_vis = dat_vis |> mutate(exam_age = (v1date01 - birthdat + exam_dat)/365.25) |>
  select(-v1date01, -birthdat, -elevel02)
```

## Associations with single Covariates
### Continous variables
```{r}
colnames(dat_vis)
cov_continous <- c("Age", "SPPB")
for (covariate in cov_continous) {
  plot_list = list()
  for (var in var_list){
    temp = dat_vis[!is.na(dat_vis[[covariate]]), ]
    name = step_algorithms[which(var_list == var)]
    plot = ggplot(dat_vis, aes(x = .data[[covariate]], y = .data[[var]])) +
      geom_smooth() +
      labs(x = covariate, y = 'Step counts per day', #paste0("Step counts (", name, ')'
           fill = covariate,
           title = name) +
      theme_minimal() + 
      custom_theme
    
    plot_list[[var]] = plot
  }
  output_name = paste0('Results/04_Continous_', covariate, '.pdf')
  
  pdf(output_name, height = 6, width = 9)
  a = plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount_ssl + plot_list$vs + 
    plot_layout(guides = "collect") &
    theme(legend.position = 'bottom')
  print(a)
  dev.off()
}
```

### Category variables with density plots
```{r}
colnames(dat_vis)
covariates <- c("Sex", "Race", "Education", "Smoking", "Drinking", 'APOE')

for (covariate in covariates) {
  plot_list = list()
  for (var in var_list) {
    temp = dat_vis[!is.na(dat_vis[[covariate]]), ]
    name = step_algorithms[which(var_list == var)]
    plot = ggplot(temp, aes(x = .data[[var]], fill = as.factor(get(covariate)))) +
      geom_density(alpha = 0.5) +
      labs(x = 'Step counts per day', y = 'Density', #paste0("Step counts (", name, ')'
           fill = covariate,
           title = name) +
      scale_y_continuous(labels = scales::scientific_format(digits = 1)) + 
      theme_minimal() + custom_theme
    
    plot_list[[var]] = plot
  }
  output_name = paste0('Results/04_Density_', covariate, '.pdf')
  
  pdf(output_name, height = 6, width = 9)
  a = plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount_ssl + plot_list$vs + 
    plot_layout(guides = "collect") &
    theme(legend.position = 'bottom')
  print(a)
  dev.off()
}
```


## Associations with Age group by covariates
### Sex, Race, Education, Smoking, Drinking
```{r}
cov_continous <- c("Sex", 'Race', 'Education', "Smoking", "Drinking", 'APOE') #SPPB
for (covariate in cov_continous ) {
  plot_list = list()
  for (var in var_list){
    temp = dat_vis[!is.na(dat_vis[[covariate]]), ]
    name = step_algorithms[which(var_list == var)]
    plot = ggplot(temp, aes(x = exam_age, y = .data[[var]], color = as.factor(get(covariate)))) +
      #geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs")) +
      geom_smooth()+
      labs(x = covariate, y = 'Step counts per day', #paste0("Step counts (", name, ')'
           fill = covariate,
           color = covariate,
           title = name) +
      theme_minimal() + 
      custom_theme
    
    plot_list[[var]] = plot
  }
  output_name = paste0('Results/05_Age_GroupBy_', covariate, '_loess.pdf')
  
  pdf(output_name, height = 6, width = 9)
  a = plot_list$adept + plot_list$oak + plot_list$sdt + plot_list$stepcount_ssl + plot_list$vs + 
    plot_layout(guides = "collect") &
    theme(legend.position = 'bottom')
  print(a)
  dev.off()
}
```

# 04.Output the datasets
```{r}
# write.csv(dat_vis, '00_Intermediate_output/02_Step_Cov_V9.csv')
```

