
# Set Parameters
```{r}
library(readr)
library(haven)
library(dplyr)
library(ggplot2)
library(DataExplorer)
library(patchwork)
library(lubridate)
library(arctools)
library(here)

custom_theme <- theme(
  panel.background = element_blank(),
  axis.ticks = element_blank(),
  axis.text = element_text(size = 12),
  axis.title = element_text(size = 12, face = "bold"),
  axis.line = element_line(size = 0.5),
  plot.title = element_text(size = 14, face = "bold", hjust = 0.5)
)

custom_theme2 <- theme(
    panel.grid.major = element_blank(),  # remove major panel lines
    panel.grid.minor = element_blank(),  # remove secondary panel lines
    panel.background = element_blank(),  # remove background colors
    axis.ticks = element_blank(),  # remove scales in axis.
    panel.border = element_rect(colour = "black", fill = NA, size = 1)  # Add border
  )

step_algorithms = c('ADEPT', 'OAK', 'SDT', 'Stepcount', 'Verisence')
```

# Check data intergrity.
```{r}
# Load full subject list
sub.list.full = read.csv(here('00_ARIC.generated.step/subject.full.csv')) |>
  mutate(subjectid = sub('_.*', '', sub('\\..*$', '', subjectid)))

# Load successfully gt3x-transformed data
sub.list.gt3x = readxl::read_xlsx(here('00_ARIC.generated.step/subject.full.gt3x.transformed.xlsx')) |>
  mutate(subjectid = sub('_.*', '', sub('\\..*$', '', subjectid)),
         gt3x.transformed = 1)

# Load TAC data.
folder.name = here('01_ARIC_TAC/')
files = list.files(folder.name)
files.name = data.frame(subjectid = sub('_.*', '', 
                                        sub('\\..*$', '', files))); files.name$TAC = 1

# Load Step data
result = read_csv(here('00_Intermediate_output/estimated_stepcounts.csv'))|>
  select(-stepcount_rf, -`...1`) |>
  mutate(subjectid = sub('_.*', '', sub('\\..*$', '', subjectid)))

# Check missing conditions
tmp = merge(sub.list.full, sub.list.gt3x, all.x = TRUE)
tmp = merge(tmp, files.name, all.x = TRUE)
tmp = merge(tmp, result, all.x = TRUE)

sum(is.na(tmp$gt3x.transformed)) # Num = 0
sum(is.na(tmp$TAC)) # Num = 17, why lose them, further check!
sum(is.na(tmp$adept)) # Num = 201
tmp[is.na(tmp$TAC),]$subjectid # The ID need to check

sum(complete.cases(tmp)) # Num = 1203
tmp[is.na(tmp$TAC),]
```

## Extract steps in the complete day
### Define functions for calculating new daily steps
```{r}
dat.step <- function(folder.path, file.name){
  algorithm.name = sub('.rds', '', sub('.csv', '', sub(".*-", "", file.name)))
  if (length(file.name) == 0){
    tmp = data.frame(NA)
    colnames(tmp)[1] = algorithm.name
    return(tmp)
  }
  
  if (length(file.name) >1 ){
    file.name = file.name[grepl('.rds', file.name)]
  }
  
  if(grepl('.csv', file.name)){
    dat = read_csv(paste0(folder.path, '/',file.name))
  } else {
    dat = readRDS(paste0(folder.path, '/',file.name))
    if (class(dat)[1] == 'list') {
      dat = dat$steps
    }
  }
  
  dat[,2][is.na(dat[,2])] = 0
  
  noon.point = unique(dat$time[format(dat$time, "%H:%M:%S") == "12:00:00"])
  first_noon <- min(noon.point)
  last_noon <- max(noon.point)
  start_index <- which(dat$time >= first_noon)[1]
  end_index <- tail(which(dat$time <= last_noon-1), n = 1)
  dat.selected <- dat[start_index:end_index,] %>%
    mutate(date = if_else(hour(time) < 12, as.Date(time) - 1, as.Date(time)))
  
  dat.selected$date = as.character(dat.selected$date)
  
  if (grepl('oak|sdt|stepcount|vs', file.name)){
    colnames(dat.selected)[grepl('step', colnames(dat.selected))] = 'steps'
    daily_totals <- dat.selected %>%
      group_by(date) %>%
      summarise(total_value = sum(steps, na.rm = TRUE)) %>%
      ungroup() %>%
      mutate(id = subid)
  } else {
    daily_totals <- dat.selected %>%
    group_by(date) %>%
    summarise(total_value = sum(!!sym(paste0('steps_', algorithm.name[1])), na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(id = subid)
  }
  
  
  colnames(daily_totals)[2] = algorithm.name
  return(daily_totals)
}
```


## Regenerate daily steps and check the missness
```{r, warning=FALSE, echo=FALSE}
folder.path = '002_Estimtaed.steps.seconds'
missing.list = data.frame(subid = NA,
                          num = NA)
for (subid in tmp$subjectid){
  which(grepl(subid, tmp$subjectid))
  folder = '002_Estimtaed.steps.seconds/'
  files = list.files(folder)
  subid = sub('[A-Z]', '', subid) # remove character to ensure the connections
  
  files.list = files[grepl(subid, files)]
  if(length(files.list) < length(step_algorithms)){
    missing.list = rbind(missing.list,
                         data.frame(subid, num = length(files.list)))
    print(subid); next
  }
  
  if (sum(grepl('stepcount', files.list))>1){
    files.list = files.list[-which(grepl('rf', files.list))]
  }
  
  result = data.frame(
    subjectid = subid,
    Date = dat.step(folder.path, files.list[grepl('adept', files.list)])$date,
    adept = dat.step(folder.path, files.list[grepl('adept', files.list)])$adept,
    oak = dat.step(folder.path, files.list[grepl('oak', files.list)])$oak,
    sdt = dat.step(folder.path, files.list[grepl('sdt', files.list)])$sdt,
    stepcount = dat.step(folder.path, files.list[grepl('stepcount', files.list)])[,2][[1]],
    verisence = dat.step(folder.path, files.list[grepl('vs', files.list)])$vs
      # [,2] stepcount_ssl and stepcount_rf have two '-' for the data we use
      # To avoid defination error, use steps number in the second column
  )
  
  write.csv(result, paste0('003_Regenerate.steps.day/', subid, '.csv'))
}

length(list.files('003_Regenerate.steps.day/')) # Num=1405
# M159416 (Num = 736), stepcount, ssl, only 6 observations, while others have 7 obs.
```

## Based on the missing list, regenerate daily steps
```{r}
missing.list[missing.list$num !=3,]
```

```{r}
folder.path = '002_Estimtaed.steps.seconds'
missing.list.2 = data.frame(subid = NA,
                          num = NA)

for (subid in missing.list$subid){
  which(grepl(subid, missing.list$subid))
  folder = '002_Estimtaed.steps.seconds/'
  files = list.files(folder)
  subid = sub('[A-Z]', '', subid) # remove character to ensure the connections
  
  files.list = files[grepl(subid, files)]
  if(length(files.list) < length(step_algorithms)){
    missing.list.2 = rbind(missing.list.2,
                         data.frame(subid, num = length(files.list)))
    print(subid); next
  }
  
  if (sum(grepl('stepcount', files.list))>1){
    files.list = files.list[-which(grepl('rf', files.list))]
  }
  
  result = data.frame(
    subjectid = subid,
    Date = dat.step(folder.path, files.list[grepl('adept', files.list)])$date,
    adept = dat.step(folder.path, files.list[grepl('adept', files.list)])$adept,
    oak = dat.step(folder.path, files.list[grepl('oak', files.list)])$oak,
    sdt = dat.step(folder.path, files.list[grepl('sdt', files.list)])$sdt,
    stepcount = dat.step(folder.path, files.list[grepl('stepcount', files.list)])[,2][[1]],
    verisence = dat.step(folder.path, files.list[grepl('vs', files.list)])$vs
      # [,2] stepcount_ssl and stepcount_rf have two '-' for the data we use
      # To avoid defination error, use steps number in the second column
  )
  
  write.csv(result, paste0('003_Regenerate.steps.day/', subid, '.csv'))
}

# 149096 (Num = 7), stepcount, ssl, only 4 observations, while others have 7 obs.
missing.list.2
```

# Check Step intergrity.
```{r}
missing.list
```

# Combine the steps again to check missing relationship with TAC
```{r}
tmp$subjectid = sub('[A-Z]', '', tmp$subjectid)
tmp$adept = NULL;tmp$oak = NULL; tmp$sdt = NULL
tmp$stepcount_ssl = NULL; tmp$vs = NULL

folder.path = '003_Regenerate.steps.day/'
file.step.names = data.frame(subjectid = sub('.csv', '', list.files(folder.path)))
file.step.names$newStep = 1


tmp.2 = merge(tmp, file.step.names, all.x = TRUE)
tmp.2[rowSums(is.na(tmp.2)) >= 1,]

TAC.list = tmp[is.na(tmp$TAC),]
# write.csv(TAC.list, '000_ARIC.generated.step/TAC.missing.csv')
```
## Check subjects who have steps but not TAC
```{r}
tmp.2[(is.na(tmp.2$TAC) + (tmp.2$newStep == 1 & !is.na(tmp.2$newStep)))==2,]
  # subjects who have steps but not TAC: Number = 11
# write.csv(tmp.2[(is.na(tmp.2$TAC) + (tmp.2$newStep == 1 & !is.na(tmp.2$newStep)))==2,],
#           'subject.step.NotTAC.csv')

## All ssituations listed as below:
# 1) TAC frequency=30Hz
# 2) Observation day less than 1 day
# No matter what conditions, these subjects were excluded in the next analysis
```

## Check subjects who have TAC but not steps
```{r}
tmp.2[(is.na(tmp.2$newStep) + (tmp.2$TAC == 1 & !is.na(tmp.2$TAC)))==2,]
# 149096: new csv file
# 159416: new csv file
```
## Check subjects who lose TAC and steps
```{r}
tmp.2[(is.na(tmp.2$TAC) + is.na(tmp.2$newStep)) ==2,]

# The conditions for these files have been explored:
## Detailed situations are shown in "miss_list_xinkai".
```

## Combine steps and TAC together to obtain final dataset
```{r}
## Error files
err.files = data.frame(subjectid = NA,
                       error = NA)

library(zoo)
library(ds4psy)
# Load TAC data
folder.name = '001_ARIC_TAC/'
files = list.files(folder.name) # Num=1394 (miss Num=11, Total = 1411)
files.steps = list.files('003_Regenerate.steps.day/')

# Summarize TAC, valid signal and steps
for (file in files){
  ## generate daily steps
  dat.TAC = readRDS(paste0(folder.name, file)) |>
    mutate(VM_mean = VM_mean*60) # VM_mean: average TAC in one second
  # check the completeness of TAC
  if (!is_wholenumber(dim(dat.TAC)[1]/1440)){
    err.files = rbind(err.files,
                      data.frame(subjectid = file, 
                                 error = 'not a multiple of 1440 (number of minutes in a day)'))
    next
  }
  dat.TAC$minute = as.POSIXct(strptime(dat.TAC$minute, format="%Y-%m-%d %H:%M:%S", tz="UTC"))

  # Add missing timestamp
  dat.TAC = dat.TAC |>
    mutate(tmp.minute = minute[1] + cumsum(rep(60, n())))
  dat.TAC$minute[is.na(dat.TAC$minute)] = dat.TAC$tmp.minute[is.na(dat.TAC$minute)]
  
  # generate daily steps
  dat.TAC <- dat.TAC %>%
    mutate(date = if_else(hour(minute) < 12, as.Date(minute) - 1, as.Date(minute)))
  TAC_totals <- dat.TAC %>%
    group_by(date) %>%
    summarise(TAC = sum(VM_mean)) %>%
    mutate(id = sub('.rds', '', file))
  
  # generate valid flag
  wear_flag <- get_wear_flag(dat.TAC$VM_mean)
  wear_flag_mat <- matrix(wear_flag, ncol = 1440, byrow = TRUE)
  valid_day_flag <- get_valid_day_flag(wear_flag)
  valid_day_flag_mat <- matrix(valid_day_flag, ncol = 1440, byrow = TRUE)
  
  TAC_totals$valid = apply(valid_day_flag_mat, 1, mean, na.rm = TRUE)
  TAC_totals = TAC_totals |> mutate(id = sub('[A-Z]' ,'', sub('.rds', '', file))) |>
    select(-id)
  
  # Add Steps to TAC
  file = sub('_.*', '', sub('[A-Z]' ,'', sub('.rds', '', file)))
  file.step = files.steps[grepl(file, files.steps)]
  dat.step = read.csv(paste0('003_Regenerate.steps.day/', file.step)); dat.step$X = NULL
  dat.step$date = as.POSIXct(dat.step$Date)
  
  dat.TAC.step = merge(TAC_totals, dat.step, by = 'date') |>
    select(-Date, subjectid, date, TAC, valid, adept, oak, sdt, stepcount, verisence)
  
  write.csv(dat.TAC.step, paste0('004_Combined.Steps.TAC/', file, '.csv'))
}
```

## Combine individual steps together
```{r}
folder.step = '004_Combined.Steps.TAC/'
file_list <- list.files(folder.step)

# Use lapply to read all files and combine them into a single DataFrame
combined_data <- do.call(rbind, lapply(file_list, function(file) {
  read.csv(paste0(folder.step, file), stringsAsFactors = FALSE)
})); combined_data$X = NULL
```

# Ouput my results
```{r}
write_csv(combined_data, '00_Intermediate_output/step.TAC.final.csv')
```

